### 2015-05-11 evaluation.tex
fix

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{0.3em}
\caption{Program statistics and race-checking results from running \whoop and \corral on our benchmarks.}
\label{tab:stats}
\begin{tabular}{l rrr rr r}
\centering
\input{experiments/tables/statistics.tex}
\end{tabular}
\end{table}

@@

\noindent
\textbf{Granularity of Context-Switches}\xspace\xspace Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks. All reported times are in seconds and averages of three runs. \corral was given a time budget of 8 hours (T.O. denotes a tool timeout) and a context-switch bound (csb) of 2, 5 and 9. By default, \corral instruments context-switches (i.e. \texttt{yield}) in all visible operations (denoted by \yieldall in the table). \whoop + \corral, instead, uses two different context-switch instrumentation granularities, \yieldcoarse and \yieldmr (see Section~\ref{whoop:bugfinding}), and also uses all the optimisations discussed in Section~\ref{whoop:optimizations}.

>>>>

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{0.3em}
\caption{Program statistics and race-checking results from applying \whoop and \corral on our benchmarks.}
\label{tab:stats}
\begin{tabular}{l rrr rr r}
\centering
\input{experiments/tables/statistics.tex}
\end{tabular}
\end{table}

@@

\noindent
\textbf{Granularity of Context-Switches}\xspace\xspace Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks. All reported times are in seconds and averages of three runs. \corral was given a time budget of 10 hours (T.O. denotes a tool timeout) and a context-switch bound (csb) of 2, 5 and 9. By default, \corral instruments context-switches (i.e. \texttt{yield}) in all visible operations (denoted by \yieldall in the table). \whoop + \corral, instead, uses two different context-switch instrumentation granularities, \yieldcoarse and \yieldmr (see Section~\ref{whoop:bugfinding}), and also uses all the optimisations discussed in Section~\ref{whoop:optimizations}.
